Working document to try to explain why/how ATAs influence coexistence in an intuitive way for referee 3

### 2023-07-12 paper/ExplanationOfATAEffectsWorkingDoc.tex
added a good explanation

\section{Ecological explanation}
Under Modern Coexistence Theory, the outcome of coexistence is determined by 
niche differences and fitness differences (Chesson 2000, Adler 2007). 
When niche differences overcome fitness differences, coexistence is possible. 
Niche differences are driven by stabalizing mechanisms (such as the storage effect), 
which are defined as mechanisms that cause a species to limit itself more than it 
limits others, i.e., the species experiences more intraspecific competition than 
interspecific competition.

The storage effect stably contributes to coexistence through 
temporal niche partitioning with EC covariance and buffered population growth.
Under invader-resident analysis [rare-common], EC covariance limits the resident by 
coupling high environmental responses with high intraspecific competition. The magnitude
of the storage effects then depends on the EC covariance of the invader. Because the 
invader is introduced into the resident steady state community at close to zero density, 
its C is only a result of interspecific competition from the resident. Thus, the more closely 
related the invader's EC relationship is, the more interspecific competition it experiences, 
destabalizing coexistence. Equivalently, invader EC relationships with more spread stably
contribute to coexistence (through the storage effect). As seen in Fig. \ref{thefig}, ATAs in the invader EC relationship changes its bivariate distribution to both have more spread about the "central line" and be more densely situated about the "central line".

>>>>

\section{Ecological explanation}
\subsection{Basic MCT}
Under Modern Coexistence Theory, the outcome of coexistence is determined by 
niche differences and fitness differences (Chesson 2000, Adler 2007). 
When niche differences overcome fitness differences, coexistence is possible. 
Niche differences are driven by stabalizing mechanisms (such as the storage effect), 
which are defined as mechanisms that cause a species to limit itself more than it 
limits others, i.e., the species experiences more intraspecific competition than 
interspecific competition.

\subsection{Storage effect and how ATAs can change it}
The storage effect stably contributes to coexistence through 
temporal niche partitioning with EC covariance and buffered population growth.
Under invader-resident analysis [rare-common], EC covariance limits the resident by 
coupling high environmental responses with high intraspecific competition. The magnitude
of the storage effects then depends on the EC covariance of the invader. Because the 
invader is introduced into the resident steady state community at close to zero density, 
its C is only a result of interspecific competition from the resident. Thus, the more closely 
related the invader's EC relationship is, the more interspecific competition it experiences, 
destabalizing coexistence. Equivalently, invader EC relationships with more spread stably
contribute to coexistence (through the storage effect). As seen in Fig. \ref{thefig}, ATAs in 
the invader EC relationship changes its bivariate distribution to both have more spread 
about the "central line" and be more densely situated about the "central line".    
When the invader's EC relationship has more spread (more density in values far away from 
the central line) than what the invader's EC relationship would be if it was symmetric, 
the ATA effect is positive. More specifically, points to the right of the central line are where environmental response is high and competition is low. When points fall in this plane, is when species can "store" the beneficial effects of a good environment to counteract when conditions are less ideal. Thus when the EC relationship is less spread, the invader is less able to recover from rare because the points are far away from the beneficial extremes. 
I think this related to the subadditivity criteria of storage effect, i.e., buffered population growth which is related to nonlinear averaging. Subaddivity/ buffered popualtion growth is when species growth rate responses to competition are less affected/sensitive to bad environmental conditions and more affected and sensitive when conditions are good. So it is nonlinear. So points in the beneficial extremes are when the invader can take advantage of the nonlinear averaging that comes with buffered population growth. ATA'd EC relationships have different distribution of points compared to one that is symmetric with the same marginals and correlation so the asymmetry changes whether or not points are in the beneficial extremes.

\subsection{How can ATAs in the EC relationship arise?}
\emph{Water limitation.} Everyone depends on water. When water is limited niches become less different. So the invader's EC relationship in low values of environmental response is more correlated to the competitive pressure it experiences from the resident since the resident is also experiencing water limitation and will be in its low environmental response values. When water is not the limiting factor, environmental responses take on higher values and thus, the EC relationship may be more spread.
